Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-02-23 presentation-plan/presentation-plan.tex
Some trivial presentation setup
added small last changes

FF-Replan is an action selection algorithm for online planning in probabilistic domains. Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem. It determinizes the input domain at the start of the planning into a deterministic different domain. They consider two methods of determinization:
\begin{enumerate}
	\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics. The performance strongly depends on the methods for choosing the outcomes.
	\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a dinstinct deterministic action. For each possible outcome  FF-Replan generates one seperate action for each effect. For nested probabilities, the all-outcomes procedure is applied recursively. This implies that FF-Replan will ceise selection actions whenever it enters a dead state. However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
\end{enumerate}

After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem. This process is repeated when countering an unexpected state untill a goal state is reached. It maintains a partial state-action mapping using a hash-table which is initially empty. Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF. It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table . The first action of the plan in then executed in the environment, returning a new state. This partial policy is this produces in an online fashion. It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.

@@

By relying on search, FF-Replan could function with enormous speed and efficiency. However when dealing with difficult probabilistic problems attempting to span the spectrum of complexity ranging from deterministic problems to highly stochastic problems, FF-Replan is expected to come short. Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors can only hope to achieve this.

@@

\section{Questions that arose}

@@

>>>>

FF-Replan is an action selection algorithm for online planning in probabilistic domains. Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem. It determinizes the input domain at the start of the planning into a deterministic different domain. They consider two methods of determinization:
\begin{enumerate}
	\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics. The performance strongly depends on the methods for choosing the outcomes.
	\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a dinstinct deterministic action. For each possible outcome  FF-Replan generates one seperate action for each effect. For nested probabilities, the all-outcomes procedure is applied recursively. This implies that FF-Replan will ceise selecting actions whenever it enters a dead state. However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
\end{enumerate}

After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem. This process is repeated when countering an unexpected state untill a goal state is reached. It maintains a partial state-action mapping using a hash-table which is initially empty. Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF. It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table. The first action of the plan is then executed in the environment, returning a new state. This partial policy is this produces in an online fashion. It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.

@@

By relying on search, FF-Replan could function with enormous speed and efficiency. However when dealing with difficult probabilistic problems attempting to span the spectrum of complexity ranging from deterministic problems to highly stochastic problems, FF-Replan is expected to come short. Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors are hoping to achieve this.

@@

@@

\begin{itemize}
	\item Introduction 
	\item Brief introduction to prior knowledge
	\item Summary of the papers
		\item Advantages and disadvantages
	\item Comparison with ideas of other papers
	\item Some initial ideas of improvements
\end{itemize}
